### 2011-07-02 Posters/NNS2011/myposter.tex
ENH: Minor edits.

\vspace{0.3em}
    \scriptsize
      \vspace{-0.4em}
      \renewcommand{\refname}{\vspace{-0.8em}}
      \bibliographystyle{abbrv}
      \bibliography{references}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Open source software}{name=software,column=1,below=conclusions,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{1mm}
  \begin{center}
  \begin{tabular}{cc}
  \includegraphics[height=18mm]{ants_logo.png} &
  \includegraphics[height=18mm]{itkLogo.jpg} \\
%  {Advanced Normalization Tools} & {Insight Toolkit} \\
  {\tiny http://www.picsl.upenn.edu/ANTs} &
%  {\tiny http://www.cs.ucl.ac.uk/research/medic/camino} &
  {\tiny http://www.itk.org/} \\
  \end{tabular}
  \end{center}

>>>>

\vspace{2mm}
    \tiny % \scriptsize
      \vspace{-0.4em}
      \renewcommand{\refname}{\vspace{-0.8em}}
      \bibliographystyle{abbrv}
      \bibliography{references}

  \begin{center}
  {\normalsize \bf Open source software} \\
{\vspace{3mm}}
  \begin{tabular}{cc}
  \includegraphics[height=12mm]{ants_logo.png} &
  \includegraphics[height=11mm]{itkLogo.jpg} \\
%  {Advanced Normalization Tools} & {Insight Toolkit} \\
  {\tiny http://www.picsl.upenn.edu/ANTs} &
%  {\tiny http://www.cs.ucl.ac.uk/research/medic/camino} &
  {\tiny http://www.itk.org/} \\
  \end{tabular}
  \end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Acknowledgments}{name=acknowledgments,column=1,below=conclusions,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{1mm}
  \scriptsize
  \begin{itemize}
  \item Partial funding support from NZ Breacher study
  \item This project is also funded, in part, under a grant with the Pennsylvania 
  Department of Health. The Department specifically disclaims responsibility 
  for any analyses, interpretations, or conclusions.
  \end{itemize}
  }
